Tropical mathematics and the Lambda-calculus I

### 2023-07-31 CSL24/section7.tex
commit

More generally, the literature on program metrics in denotational semantics is vast. Since at least \cite{VANBREUGEL20011} metric spaces, also in Lawvere's generalized sense \cite{Lawvere1973}, have been exploited as an alternative framework to standard, domain-theoretic, denotational semantics, notably
\emph{ultra}-metrics and \emph{partial} metrics have been shown to form a CCC \cite{Escardo1999,PistoneLICS, PistoneFSCD2022}.

>>>>

More generally, the literature on program metrics in denotational semantics is vast. Since at least \cite{VANBREUGEL20011} metric spaces, also in Lawvere's generalized sense \cite{Lawvere1973}, have been exploited as an alternative framework to standard, domain-theoretic, denotational semantics; notably models of $\STLC$ and $\mathrm{PCF}$ based on 
\emph{ultra}-metrics and \emph{partial} metrics have been proposed  \cite{Escardo1999,PistoneLICS, PistoneFSCD2022}.
